IoT - Ethernet APL\\

### 2022-01-10 Research Paper on Ethernet APL/paper.tex
Last milestone

\author{\IEEEauthorblockN{ Giuseppe Scalora}
\IEEEauthorblockA{\textit{Electronic Engineering} \\
\textit{Hochschule Hamm-lippstadt}\\
Lippstadt, Germany \\
giuseppe.scalora@stud.hshl.de}

@@

\section{Main applications}
\section{Conclusion}

\begin{thebibliography}{00}
\bibitem{b1} https://www.analog.com/en/thought-leadership/ethernet-apl-optimization-of-process-automation.html
\bibitem{b2} C. Spurgeon, Ethernet. Beijing: O'Reilly, 2009.
\bibitem{b3} https://www.educba.com/what-is-osi-model/
\bibitem{b4} https://www.networkworld.com/article/3239677/the-osi-model-explained-and-how-to-easily-remember-its-7-layers.html
\bibitem{b5} https://en.wikipedia.org/wiki/OSI\_model
\bibitem{b6} https://www.controlglobal.com/articles/2020/advanced-physical-layer-standard-to-make-field-level-ethernet-a-reality/
\bibitem{b7} https://www.pepperl-fuchs.com/italy/it/41850.htm
\bibitem{b8} https://static1.squarespace.com/static/5c33ae96f407b4bfc5884978/t/60c7ef3a4807d14ca771825d/1623715647354/Ethernet-APL\_Ethernet-To-The-Field\_EN\_FINAL\_June-2021.pdf
\bibitem{b9} https://www.automationworld.com/communication/article/21545085/industrial-ethernet-advances-broaden-the-networks-value-across-industries
\bibitem{b10} Whitepaper Ethernet-APL in the Field for
high-availability Safety Applications
\end{thebibliography}

>>>>

\author{\IEEEauthorblockN{ Giuseppe Scalora}
\IEEEauthorblockA{\textit{Electronic Engineering} \\
\textit{Hochschule Hamm-lippstadt}\\
Lippstadt, Germany \\
giuseppe.scalora@stud.hshl.de, 10.01.2022}

@@

\section{Main application and importance in process plants}
An important statement comes from the technological leader Pepperl-Fuchs. According to this technological giant, industry 4.0 and IIoT have been longly part of daily life. Although in smart factories it has been a problem because of the lack of high speed end to end data transmission. This lack is of course filled by the advent of APL Ethernet. According to this, Pepperl-Fuchs suggests that in the near future an extensive use of APL will be applied to process plants.
Let us now take a look at this main application of the Ethernet APL for IoT purposes and industrial purposes.
The main application of Ethernet APL in a plant is touching one of the most important plant related topics, which is efficiency. For a plant to be efficient, it must be reliable, able to inform and provide data for future maintenance of tools and instrumentation, must be easy to diagnose if any accident happens and needs to be flexible to work with different devices manufacturers. Continuous collection of data in real time makes sure that APL supports all the mentioned requirements of a plant. Let us see how APL does that in a real world application:
\begin{itemize}
\item APL provides reliability as a well proven ethernet standard as it has been a standard for many years in the IT world, useful for hybrid and process automation.
\item APL is highly available as the protocol features availability concepts like system redundancy or media redundancy for cable accidents.
\item Predictive maintenance provided by the APL protocol includes all the smart field devices which make sure the communication renders the data accessible and available for status monitoring and condition monitoring.
\item Ethernet technology provides for easy network diagnostic tools to identify causes of failures and accidents and keep track of the current status of any switch or front/end device in the system.
\item Lastly, but not in importance, the interoperability provided by APL ensures the correct working functionalities of devices from different manufacturers and vendors.
\end{itemize}
The access to field data activates new digital services needed by the business management of the process plant. By an extensive inclusion of IIoT technology it provides real time feedbacks and information.

\section{Conclusion}
The idea of having an ethernet with an advanced physical layer is indeed a great step towards an internet communication protocol which could bring and lead to amazing improvements in the field. With its main characteristics compared to other protocols it is clear that as soon as it will become a more standardized communication mean, it will overtake even its competitors. Now the paper has given a broad enough overview and bit of information necessary as an input for further research of the topic. Leaders of technological corporations are collaborating in order to finalize the process of delivery for the APL and we might see even a broader range of applications very soon as shown in the delivery roadmap below for the APL.
\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.45]{apllaunchroadmap.png}}
    \caption{Roadmap for development of APL \cite{b8}}
    \label{rmapl}
\end{figure}

\begin{thebibliography}{00}
\bibitem{b1} https://www.analog.com/en/thought-leadership/ethernet-apl-optimization-of-process-automation.html
\bibitem{b2} C. Spurgeon, Ethernet. Beijing: O'Reilly, 2009.
\bibitem{b3} https://www.educba.com/what-is-osi-model/
\bibitem{b4} https://www.networkworld.com/article/3239677/the-osi-model-explained-and-how-to-easily-remember-its-7-layers.html
\bibitem{b5} https://en.wikipedia.org/wiki/OSI\_model
\bibitem{b6} https://www.controlglobal.com/articles/2020/advanced-physical-layer-standard-to-make-field-level-ethernet-a-reality/
\bibitem{b7} https://www.pepperl-fuchs.com/italy/it/41850.htm
\bibitem{b8} https://www.ethernet-apl.org/
\bibitem{b9} https://www.automationworld.com/communication/article/21545085/industrial-ethernet-advances-broaden-the-networks-value-across-industries
\bibitem{b10} Whitepaper Ethernet-APL in the Field for
high-availability Safety Applications
\end{thebibliography}
